---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hivscore

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/jaromilfrossard/hivscore/branch/master/graph/badge.svg)](https://app.codecov.io/gh/jaromilfrossard/hivscore?branch=master)
<!-- badges: end -->

The `hivscore` package is an implementation of the VACS Index 1, the VACS Index 2 and the Dat'AIDS score.

## Installation

You can install the development version of the `hivscore` package like so:

``` r
remotes::install_github("jaromilfrossard/hivscore")
```

## Computing the scores

You can compute the VACS Index 1:

```{r ex_v1}
library(hivscore)
data("vacs1")
vacs1$score_vacs1 <- score_vacsindex1(
  age = vacs1$age, cd4_count = vacs1$cd4, hiv1_rna = vacs1$hiv1_rna,
  hgb = vacs1$hgb, fib4 = vacs1$fib4, egfr = vacs1$egfr,
  hepc = vacs1$hepc)
head(vacs1)
```

For the VACS Index 2, you will use:

```{r ex_v2}
data("vacs2")
vacs2$score_vacs2 <- score_vacsindex2(
  age = vacs2$AGE, cd4_count = vacs2$CD4,vl_log = vacs2$VL_LOG,
  hgb = vacs2$HGB,fib4 = vacs2$FIB4,egfr = vacs2$EGFR,
  hepc = vacs2$HEPC==1, alb = vacs2$ALB, bmi = vacs2$BMI,
  wbc = vacs2$WBC)
head(vacs2)
```

The Dat'AIDS score can be computed using:
```{r ex_dataids}
data("dataids")
dataids$dataids <- score_dataids(
  age = dataids$age,cd4_count = dataids$cd4_count, nonhiv_cancer = dataids$nonhiv_cancer,
  cardio_disease = dataids$cardio_disease,egfr = dataids$egfr, cirrhosis = dataids$cirrhosis,
  low_bmi = dataids$low_bmi,anemia = dataids$anemia)
head(dataids)
```

## Predicting survival probabilities

Using the Dat'AIDS score, you can predict survival probabilities after 1 year:

```{r ex_surv}
dataids$surv_prob1 <- surv_dataids(1, score = dataids$dataids)
head(dataids)
```


## References

For the VACS Index 1:

- Tate, J. P., Justice, A. C., Hughes, M. D., Bonnet, F., Reiss, P., Mocroft, A., ... & Sterne, J. A. (2013). An internationally generalizable risk index for mortality after one year of antiretroviral therapy. AIDS (London, England), 27(4), 563.
- Bebu, I., Tate, J., Rimland, D., Mesner, O., Macalino, G. E., Ganesan, A., ... & Infectious Disease Clinical Research Program HIV Working Group. (2014). The VACS index predicts mortality in a young, healthy HIV population starting highly active antiretroviral therapy. Journal of acquired immune deficiency syndromes (1999), 65(2), 226.
- Justice, A. C., Modur, S., Tate, J. P., Althoff, K. N., Jacobson, L. P., Gebo, K., ... & Gange, S. J. (2013). Predictive accuracy of the Veterans Aging Cohort Study (VACS) index for mortality with HIV infection: a north American cross cohort analysis. Journal of acquired immune deficiency syndromes (1999), 62(2), 149.

For the VACS Index 2:

- Tate, J. P., Sterne, J. A., Justice, A. C., Study, V. A. C., & Antiretroviral Therapy Cohort Collaboration (ART-CC. (2019). Albumin, white blood cell count, and body mass index improve discrimination of mortality in HIV-positive individuals. AIDS (London, England), 33(5), 903.
- McGinnis, K. A., Justice, A. C., Moore, R. D., Silverberg, M. J., Althoff, K. N., Karris, M., ... & Study, V. A. C. (2021). Discrimination And Calibration Of The Vacs Index 2.0 For Predicting Mortality Among People With Hiv In North America. Clinical Infectious Diseases: an Official Publication of the Infectious Diseases Society of America.

For the Dat'AIDS score:

- Hentzien M, Delpierre C, Pugliese P, Allavena C, Jacomet C, Valantin M-A, et al. (2018) Derivation and internal validation of a mortality risk index for aged people living with HIV: The Dat'AIDS score. PLoS ONE 13(4): e0195725. https://doi.org/10.1371/journal.pone.0195725

